Estimating duration in the presence of misclassification

### 2024-02-07 biology-data.tex

\subsubsection{Estimating positivity rate}

@@

    This figure has been provided as management information for operational planning purposes. They are provisional estimates circulated before public release. This management information should not be shared widely and should only be used for operational planning purposes. This information is not to be used publicly and ahead of being released publicly by ONS.
  }
  \label{biology-data:fig:episodes}
\end{figure}
  \todo{Work out what to do with this figure....}

>>>>

\subsubsection{Estimating positivity rate} \label{biology-data:sec:posivity}

@@

    This figure has been provided as management information for operational planning purposes. They are provisional estimates circulated before public release. This management information should not be shared widely and should only be used for operational planning purposes. This information is not to be used publicly and ahead of being released publicly by ONS.
  }
  \label{biology-data:fig:episodes}
\end{figure}

\todo[inline]{%
    From chapter 7 add info on: how this is aggregated, SRS limitations, definitions for each episode (sketched below).
}

The beginning of episode $i$ is known to occur in the interval $[l_i^{(b)}, r_i^{(b)}]$, and similarly for the end of the infection in $[l_i^{(e)}, r_i^{(e)}]$.
